%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Key Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Dissertation| Advisor: { \color{awesome} \href{https://www.cse.iitb.ac.in/~suyash/}{Prof. Awate} } and { \color{awesome} \href{https://www.ee.iitb.ac.in/wiki/faculty/merchant}{Prof. Merchant} } } % Project subtitle title
    {A Bayesian Framework For Removal of Speckles, Smoke, and Noise in Laparoscopy Images} % Title
    {IIT Bombay} % Location
    {Apr. 2016 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modelled the uncorrupted image and smoke transmission map using Markov random fields}
        \item {Designed novel texture-preserving dictionary-based prior and color distribution prior on the training set and used them as potential functions for the graphical models}
        \item {Developed an expectation-maximation based algorithm using variational factorization to infer the uncorrupted image, beating the combination of state-of-the-art in individual corruption solving algorithms}
        \item {Awarded an oral presentation at IEEE ISBI 2017. Paper { \color{awesome} \href{https://ieeexplore.ieee.org/abstract/document/7950623}{here} } }
      \end{cvitems}
    }

	\cventry
	{Course Project| Advisor: { \color{awesome} \href{https://www.cse.iitb.ac.in/~ajitvr/}{Prof. Rajwade} } } % Project subtitle title
	{Fish recognition using point set registration} % Title
	{IIT Bombay} % Location
	{Apr. 2016 - Jun. 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed an algorithm to smoothen the boundary and autonomously place points to efficiently capture curvature of dorsal images of fish}
			\item {Evaluated the classfication performance using iterative closest point matching, robust point matching, and kernel correlation algorithms}
		\end{cvitems}
	}

\end{cventries}
